---
title: "Migraine PubMed"
author: "Janis Corona"
date: "12/9/2019"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

## This script takes twenty articles from the abstracts on Migraine articles from NCBI's PubMed


This creates a directory to stem the abstracts and preprocess from the csv file
into a corpus of 10 files in a folder called Migraines.
```{r, message=FALSE, error=FALSE, warning=FALSE}
Auto <- read.csv('migraines_PubMed_abstracts.csv', sep=',',
                 header=TRUE, na.strings=c('',' '))
colnames(Auto) 

auto <- Auto[complete.cases(Auto$abstract),]


dir.create('./Migraines')

ea <- as.character(auto$abstract)
setwd('./Migraines')

for (j in 1:length(ea)){
  write(ea[j], paste(paste('EA',j, sep='.'), '.txt', sep=''))
}
setwd('../')


```

This code preprocesses and stems the corpus
```{r, error=FALSE, warning=FALSE, message=FALSE}
library(tm)
library(SnowballC)
library(wordcloud)
library(ggplot2)

migraine <- Corpus(DirSource("Migraines"))


migraine

migraine <- tm_map(migraine, removePunctuation)
migraine <- tm_map(migraine, removeNumbers)
migraine <- tm_map(migraine, tolower)
migraine <- tm_map(migraine, removeWords, stopwords("english"))
migraine <- tm_map(migraine, stripWhitespace)
migraine <- tm_map(migraine, stemDocument)

dtmmigraine <- DocumentTermMatrix(migraine)

freq <- colSums(as.matrix(dtmmigraine))

```

This code orders words stemmed by frequency and finds input correlations
```{r}
FREQ <- data.frame(freq)
ord <- order(freq, decreasing=TRUE)

freq[head(ord, 25)]
```

```{r}

findAssocs(dtmmigraine, "criteria", corlimit=0.75)

```


```{r}
findAssocs(dtmmigraine, "disabl", corlimit=0.63)

```


```{r}
findAssocs(dtmmigraine, "women", corlimit=0.7)
```


```{r, width=500, height=500}
wf <- data.frame(word=names(freq), freq=freq)
p <- ggplot(subset(wf, freq>30), aes(word, freq))
p <- p + geom_bar(stat= 'identity') 
p <- p + theme(axis.text.x=element_text(angle=90, hjust=1)) 
p

```


```{r}
wordcloud(names(freq), freq, min.freq=25,colors=brewer.pal(3,'Dark2'))

```


```{r}
wordcloud(names(freq), freq, max.words=40,colors=brewer.pal(6,'Dark2'))

```

### The above stemmed the corpus, this will lemmatize the original csv file
and add the field to the table and write out to csv, followed by plot the 
word count frequencies that were lemmatized and the word clouds

```{r, error=FALSE, message=FALSE, warning=FALSE}
library(textstem)

lemma <- lemmatize_strings(auto$abstract, dictionary=lexicon::hash_lemmas)

Lemma <- as.data.frame(lemma)
Lemma <- cbind(Lemma, auto)

colnames(Lemma) <- c('lemmatizedAbstract','abstract', 'source')

write.csv(Lemma, 'Lemmatizedmigraine.csv', row.names=FALSE)

```

```{r, error=FALSE, message=FALSE, warning=FALSE}
dir.create('./migraine-Lemma')

ea <- as.character(Lemma$lemmatizedAbstract)
setwd('./migraine-Lemma')

for (j in 1:length(ea)){
  write(ea[j], paste(paste('EAL',j, sep='.'), '.txt', sep=''))
}
setwd('../')

```

```{r, error=FALSE, message=FALSE, warning=FALSE}
library(tm)
library(SnowballC)
library(wordcloud)
library(ggplot2)

```



```{r}
migraine <- Corpus(DirSource("migraine-Lemma"))

migraine

# this is an NCBI file so there are dashes and numbers in gene names at times
# that I would like to show, if they are frequent
# migraine <- tm_map(migraine, removePunctuation)
# migraine <- tm_map(migraine, removeNumbers)

migraine <- tm_map(migraine, tolower)
migraine <- tm_map(migraine, removeWords, stopwords("english"))
migraine <- tm_map(migraine, stripWhitespace)

dtmmigraine <- DocumentTermMatrix(migraine)
dtmmigraine

```

```{r}
freq <- colSums(as.matrix(dtmmigraine))

FREQ <- data.frame(freq)
ord <- order(freq, decreasing=TRUE)

freq[head(ord, 25)]

```


```{r}
health <- as.data.frame(findAssocs(dtmmigraine, "health", corlimit=0.6))

criteria <- as.data.frame(findAssocs(dtmmigraine, "criteria", corlimit=0.55))


treatment <- as.data.frame(findAssocs(dtmmigraine, "treatment", corlimit=0.55))

health
criteria
treatment
```

```{r, width=500, height=500}
wf <- data.frame(word=names(freq), freq=freq)
p <- ggplot(subset(wf, freq>25), aes(word, freq))
p <- p + geom_bar(stat= 'identity') 
p <- p + theme(axis.text.x=element_text(angle=90, hjust=1)) 
p

```

```{r}
wordcloud(names(freq), freq, min.freq=25,colors=brewer.pal(3,'Dark2'))

```

```{r}
wordcloud(names(freq), freq, max.words=40,colors=brewer.pal(6,'Dark2'))

```

