---
title: "Thoracic Outlet Syndrome Articles and Abstracts"
author: "Janis Corona"
date: "12/12/2019"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

## This script takes articles or abstracts on Thoracic Outlet Syndrome-TOS from PubMed or Google Scholar


This creates a directory to stem the abstracts and preprocess from the csv file
into a corpus of files in a folder called TOS.
```{r, error=FALSE, message=FALSE, warning=FALSE}
Auto <- read.csv('ThoracicOutletSyndrome.csv', sep=',',
                 header=TRUE, na.strings=c('',' ','NA'))
```

```{r, error=FALSE, message=FALSE, warning=FALSE}
auto <- Auto[complete.cases(Auto$article),]


dir.create('./TOS')

ea <- as.character(auto$article)
setwd('./TOS')

for (j in 1:length(ea)){
  write(ea[j], paste(paste('EA',j, sep='.'), '.txt', sep=''))
}
setwd('../')


```

This code preprocesses and stems the corpus
```{r, error=FALSE, warning=FALSE, message=FALSE}
library(tm)
library(SnowballC)
library(wordcloud)
library(ggplot2)

TOS <- Corpus(DirSource("TOS"))


TOS

TOS <- tm_map(TOS, removePunctuation)
#TOS <- tm_map(TOS, removeNumbers)
TOS <- tm_map(TOS, tolower)
TOS <- tm_map(TOS, removeWords, stopwords("english"))
TOS <- tm_map(TOS, stripWhitespace)
TOS <- tm_map(TOS, stemDocument)

dtmTOS <- DocumentTermMatrix(TOS)

freq <- colSums(as.matrix(dtmTOS))

```

This code orders words stemmed by frequency and finds input correlations
```{r}
FREQ <- data.frame(freq)
ord <- order(freq, decreasing=TRUE)

freq[head(ord, 25)]


```


```{r}
findAssocs(dtmTOS, "patient", corlimit=0.7)

```


```{r}
findAssocs(dtmTOS, "pain", corlimit=0.9)
```


```{r}
wf <- data.frame(word=names(freq), freq=freq)
p <- ggplot(subset(wf, freq>50), aes(word, freq))
p <- p + geom_bar(stat= 'identity') 
p <- p + theme(axis.text.x=element_text(angle=90, hjust=1)) 
p

```


```{r}
wordcloud(names(freq), freq, min.freq=48,colors=brewer.pal(3,'Dark2'))

```


```{r}
wordcloud(names(freq), freq, max.words=30,colors=brewer.pal(6,'Dark2'))

```

### The above stemmed the corpus, this will lemmatize the original csv file
and add the field to the table and write out to csv, followed by plot the 
word count frequencies that were lemmatized and the word clouds

```{r, error=FALSE, message=FALSE, warning=FALSE}
library(textstem)

lemma <- lemmatize_strings(auto$article, dictionary=lexicon::hash_lemmas)

Lemma <- as.data.frame(lemma)
Lemma <- cbind(Lemma, auto)

colnames(Lemma) <- c('lemmatizedAbstract','article', 'source')

write.csv(Lemma, 'LemmatizedTOS.csv', row.names=FALSE)

```

```{r, error=FALSE, message=FALSE, warning=FALSE}
dir.create('./TOS-Lemma')

ea <- as.character(Lemma$lemmatizedAbstract)
setwd('./TOS-Lemma')

for (j in 1:length(ea)){
  write(ea[j], paste(paste('EAL',j, sep='.'), '.txt', sep=''))
}
setwd('../')

```

```{r, error=FALSE, message=FALSE, warning=FALSE}
library(tm)
library(SnowballC)
library(wordcloud)
library(ggplot2)

```



```{r}
TOS <- Corpus(DirSource("TOS-Lemma"))

TOS

TOS <- tm_map(TOS, removePunctuation)
#TOS <- tm_map(TOS, removeNumbers)
TOS <- tm_map(TOS, tolower)
TOS <- tm_map(TOS, removeWords, stopwords("english"))
TOS <- tm_map(TOS, stripWhitespace)

dtmTOS <- DocumentTermMatrix(TOS)
dtmTOS

```

```{r}
freq <- colSums(as.matrix(dtmTOS))

FREQ <- data.frame(freq)
ord <- order(freq, decreasing=TRUE)

freq[head(ord, 25)]

```


```{r}
pain <- as.data.frame(findAssocs(dtmTOS, "pain", corlimit=0.9))

symptom <- as.data.frame(findAssocs(dtmTOS, "symptom", corlimit=0.95))


treatment <- as.data.frame(findAssocs(dtmTOS, "treatment", corlimit=0.61))

pain
symptom
treatment
```

```{r, width=500, height=500}
wf <- data.frame(word=names(freq), freq=freq)
p <- ggplot(subset(wf, freq>50), aes(word, freq))
p <- p + geom_bar(stat= 'identity') 
p <- p + theme(axis.text.x=element_text(angle=90, hjust=1)) 
p

```

```{r}
wordcloud(names(freq), freq, min.freq=50,colors=brewer.pal(3,'Dark2'))

```

```{r}
wordcloud(names(freq), freq, max.words=30,colors=brewer.pal(6,'Dark2'))

```

